---
title:  |
        | Electoral Systems, Competition, and Incentives for Corruption
author: 
  - Umberto Mignozzetti[^umberto]
date: \today
thanks: "I thank Livio DiLonardo, Sandy Gordon, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Adam Przeworski, Howard Rosenthal, Renard Sexton, Denis Stukal, and Scott Tyson for their comments. I also thank participants at APSA, MPSA, and SPSA. All materials required to replicate this study are available at <https://github.com/umbertomig/electoral-systems-corruption>."
abstract: "What are the effects of electoral systems and competition on political corruption? In this paper, I propose a formal model of political corruption where incumbents decide how much kickbacks to add in the XXXX, and challengers may run anti-corruption campaigns against the incumbents. To understand how institutions and competition affect the results, I study two benchmarks: in the first, called the non-excludable anti-corruption campaign, successful exposure of an incumbent opens her seats to all other competitors. In the second benchmark, the excludable anti-corruption campaign, the politician successfully exposing the corruption signals competence, and voters tend to prefer her vis-a-vis the other challengers. When anti-corruption campaigns are non-excludable, an increase in the number of challengers or incumbents monotonically raises corruption. However, when anti-corruption campaigns are excludable, the number of challengers is endogenously limited. The excludability makes the free-riding in corruption exposure disappear. When I increase the number of incumbents, corruption rises less than in the non-excludable benchmark. These predictions hold empirically using quasi-experimental data from Brazilian and Italian municipalities. This study has implications for the design of electoral institutions and entry barriers in democratic elections."
abstractspacing: double
keywords: Political Corruption; District Magnitude; Single-member districts; Multi-member districts; Welfare; Brazil
#jelcodes: HXXXX
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
# XXXX
```

[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

\newpage

# Introduction
\label{sec:intro}

Corruption is one of the most prevalent and harmful XXXX of developing countries. 2B2

One distinctive characteristic of corruption activity is the actor perpetrating corruption. While bureaucratic corruption may be more frequent, it is also easier to sanction and to punish. Political corruption, on the other hand, involves higher rents than bribes to access public services. Political corruption is associated with XXXX large government contracts and procurement \citep{broms2019political}, have a more disruptive effects on trust in political institutions \citep{rose2001trust, sole2018trust}, and divert the bureaucracy toward rent seeking \citep{brierley2020unprincipled}. For instance, one of the major corruption scandals in the world, the Car Wash scandal in Brazil, involved more than 50 politicians, several high level bureaucrats, and about five billion US dollars in kickbacks \citep{watts2017operation}. Given the XXXX of political corruption, it is essential to create mechanisms to sanction corrupt politicians involved in wrongdoings. 

In democracies, elections are the primary mechanism to sanction politicians \citep{XXXX}. In most free and fair democracies, politicians can still manipulate XXXX, XXXX, and sometimes even the XXXX. This lowers the effectiveness of the XXXX. In this context, this paper XXXX. 

However, many XXXX makes voters XXXX \citep{klavsnja2017uninformed, canete2020voting, janezic2020eliciting}.  , are there electoral system features that could improve the sanctioning and lower corruption? This paper studies the XXXX. 

I investigate the interplay between the number of incumbents in a polity (electoral district sizes), the number of competitors challenging those incumbents (competitiveness), and the incentives incumbents have for engaging in corruption. I propose a model where incumbents know the optimal level of investment required for public goods provision, but challengers only see the amount that incumbents spend. Incumbents have privileged information because they are inside the government, and receive information from governmental agencies. When they propose an investment higher than the optimal amount, the public goods is provided, and they pocket the difference between the optimal amount and their proposed expenditure. Thus, in this paper, the difference between the optimal and the proposed investment is the definition of political corruption.

Challengers have incomplete information about the required investment in public goods provision, but they may decide to run a negative campaign against incumbents. Challengers have a prior expectation regarding the optimal investments, and they know that the higher the expenditure proposed, the more the chances that incumbents are extracting rents. They decide to run a negative campaign that aims to gather information supporting that a given incumbent is corrupt. To run a negative campaign is costly, both in terms of collecting information, and also in terms of opportunity costs of decreasing the focus on positive proposals \citep{haselmayer2019negative}. The extent through which the negative campaign is successful depends on the rents extracted by incumbents: While voters know that challengers may accuse an honest incumbent of corruption, the amount of evidence shown to voters can tilt the perception that a given incumbent is honest, triggering his or her dismissal.

By manipulate the parameters in the model, I show that increase district magnitude increases the equilibrium level of political corruption. This because more incumbents promote coordination failures in the challengers' negative campaigning. For example, in an electoral system with one incumbent, this incumbent is the sole target of all negative campaign. In a system with two incumbents, one incumbent may be targeted with all negative campaign while the other may receive no attacks. These coordination shortcomings make the incumbents to propose higher expenditures, increasing corruption.

The effects of competition are less straightforward, and depend on how voters behave in face of a successful incumbent exposure. I investigate two behavioral mechanisms: \textit{Excludable} versus \textit{non-excludable} negative campaigning. In the \textit{excludable} negative campaign, if voters transfer the political support from the corrupt incumbent to the challenger that ran the negative campaign, then the political corruption decreases. This because the reward in denouncing a corrupt incumbent makes challengers more prone to run negative campaigns. More challengers mean more negative campaigning in equilibrium, and incumbents respond by proposing expenditures closer to the optimal spending level. On the other hand, in the \textit{non-excludable} negative campaign if voters, upon being convinced that the incumbent is corrupt, decide to randomly elect one challenger, then political corruption increases. This because randomly select the challenger that substitute the corrupt incumbent creates a free-riding incentive: every challenger prefers that other challengers pay the cost of negative campaign.

This model innovates in four aspects. First, it provides a consistent and comparable definition of corruption. Despite the evidence that corruption is detrimental for countries, corruption is poorly defined. Studies have shown that there is wide variation, even within countries, in which acts are perceived as corruption \citep{peters1978political}. \citet{barr2010corruption} show that the propensity engage in corruption can be predicted by education and corruption in the country of origin. The variation is also pronounced in the willingness to punish corrupt behavior \citep{cameron2009propensities}. Despite the variability, reporting a higher than necessary cost of providing a public good seem to be overwhelmingly accepted as corruption \citep{peters1978political}.

Second, this paper builds on the literature on electoral systems and corruption by proposing a simple model of the trade-offs involved in electoral rules choices. : Number of seats and entry barriers.

Third, my model abstracts away from other political concerns, focusing only on features of the relationship between number of challengers and number of incumbents. Recent papers have shown that corruption correlates with ideology \citep{XXXX}, in-group behavior \citep{XXXX}, and XXXX. Despite the importance of these XXXX, removing these considerations is fundamental for understanding how electoral rules affect corruption. For example, by having ideology and district size in the same model, we would be uncertain about which component (or even if the interaction between them) leads to corruption. Moreover, high polarization correlates with less punishment of corruption \citep{XXXX}, but it is unrealistic to prescribe that voters should depolarize as a way to lower corruption. The relation between polarization, ideology, and or in-group sentiments are features of the society that need to be studied in and on themselves. The strength of my model is to abstract away from these concerns, and constructing a lean model of XXXX.

Finally, differences in the behavioral mechanism that voters use to reward challengers explain the empirical variations in corruption. In polities with widespread corruption, successfully exposing a corrupt politician have a small signaling effect \citep{pavao2018corruption}. This because the electorate considers the politician exposing the corrupt incumbent as as also corrupt. In these systems, increasing competition also increase the equilibrium corruption. Conversely, in countries with low corruption, voters may reward the politician exposing the corrupt incumbent. This creates an incentive for politicians to run negative campaigns, making incumbents to extract less rents in equilibrium.

# Electoral Rules and Corruption

XXXX

# Formal Model
\label{sec:theorymodel}

Consider a strategic interaction between three players: an incumbent politician ($I$), a challenger politician ($C$), and a representative voter ($V$).

The game starts in the \textit{governing stage}, with the incumbent deciding the governmental investment in public goods provision. Incumbents have a budget $R$ units, and they choose the level of investment in public goods between zero and $R$. To decide about the investment, they receive privileged information from governmental agencies about the optimal investment required to maximize voters' welfare. For example, if a politician is deciding the funding for a governmental agency, the optimal budget is the amount that makes the agency to function perfectly. Less resources than needed could decrease significantly the quality of services but more resources than needed would not improve the services much. In technical terms, the optimal amount of service provision is a random variable $\theta \in [0, R]$, that is drawn before the game starts, and it is informed to the incumbent after she wins the election. I assume that the optimal level of expenditure is drawn from a uniform probability distribution, with support in $[0, R]$.\footnote{In the online companion of this paper, I solve the model for a generic probability density function $f$, and lay down the conditions for an equilibrium.}

When deciding the public goods provision, the incumbent can choose to invest more or less money then the optimal investment level. If the incumbent decides to invest less money, I assume that the goods are not provided. This simplification matches the reality in most cases where restricting investments can cripple the entirety of the service provision. Conversely, when the incumbent proposes an expenditure higher than the required investment, I assume she pockets the difference between the proposed and the optimal expenditure. This assumption has two implications: first, the public goods are always provided, satisfying the voters' needs; second, the incumbent has an excuse and a method to extract rents. Although corruption that ensures public goods provision seem counter-intuitive, the whole principle of kickbacks presumes that the service provision is materialized. For instance, during the 2016 Brazilian World Cup, the stadiums constructed with public money were delivered for the world cup, despite the fact that they costed 1.5 to 2.5 times more than comparable stadiums in less corrupt countries \citep{XXXX}.

After the governing stage, it starts the \textit{campaign stage}. During the campaign, the incumbent faces a challenger in an election with two characteristics. First, voters have a incumbent-bias, so that they prefer to reelect incumbents for sure when the public goods were successfully provided. This correlates with incumbency advantage findings \citep{XXXX} as well as formal models of public service provision \citep{XXXX}. Second, I assume that challengers have only one campaign instrument at their disposal: to use negative campaign against the incumbent, expose their malfeasance if present, and receive the benefits from the denouncing. Although this seems unrealistic, having only one campaign strategy helps us focus on to what extent this strategy will be employed. Moreover, when the challenger decides to run negative campaign against an incumbent, she pays a value $c>0$. This value captures the direct costs of collecting information about corruption, and also XXXX.

Finally, the last stage of the game features the representative voter observing the information gathered by the challengers, and deciding whether to sanction the incumbent. Challengers have an incentive to run negative campaign against incumbents, regardless of whether the incumbent engaged in corruption. The voters, knowing the challenger's incentives to falsely accuse incumbents, evaluate the presented evidence. The strength of the evidence correlates with the difference between the optimal expenditure and the proposed expenditure. Voters and challengers do not know the optimal expenditure, but the greater the distance between the optimal and the enacted expenditures, the easier for challengers to convince voters that the incumbents are corrupt. This assumption has empirical support is most accounting literature, as the higher the kickbacks, the harder it is to hide it from authorities \citep{XXXX}.

The timeline for this model is as follows:

\begin{enumerate}
 \item Nature draws the optimal investment level to provide the public services.
 \item The incumbent observes the optimal investment level and chooses the government investment in public goods.
 \item After the public goods provision, the election starts with the challenger choosing her campaign strategy.
 \item Voters observe the campaign and choose whether to retain or dismiss the incumbent.
\end{enumerate}

To differentiate between strategies and actions, I assume that the incumbent's decision for the expenditure is a function $\varepsilon: [0,R] \rightarrow [0,R]$, i. e., the decision-making process receives the information about the optimal level of public goods provision, and returns the expenditure decision. For the challenger there is a similar reasoning, and the decision to investigate the incumbent is a function $\varphi: [0,R] \rightarrow [0,1]$, that receives the expenditure decision and returns a probability of running the negative campaign. Condensing the discussion above, the incumbent, upon observing the optimal public goods provision level $\theta \in [0,R]$, decides the expenditure $\varepsilon \in [0,R]$. The benefits from pocketing resources are captured by a function $u(.)$. In the main paper, I assume it is equal to the identity function but that in the appendix I solve the model for a generic concave function. The expected utility of the incumbent also adds the benefit from winning the election $B>0$ times the probability of this event, given the optimal and enacted expenditures and the decision to investigate $\varphi$.

\[
U_I (\varepsilon; \theta, \varphi) \ = \ u(\varepsilon - \theta) + B \mathbb{P} (\text{re-election}; \varepsilon, \theta, \varphi) 
\]

The expected utility for the challenger involves a decision in terms of the probability to win the election and the costs of running a negative campaign. This benefit from holding office  $B>0$ is multiplied by the probability that the challenger replaces the incumbent.\footnote{I assume the material and non-material benefits from office the same for both the challenger and the incumbent. This simplifies the exposition, and makes it easier to think about these benefits as salaries or other types of pecuniary benefits.} The probability that the challenger wins the election depend on the decision to run a negative campaign, the enacted expenditure, and on her beliefs about the optimal expenditure, when she observes the enacted expenditure. The beliefs are captured by a probability rule $\mu(\theta|\varepsilon)$. The challenger also decides the investigation strategy $\varphi \in [0,R]$, and if she undertakes the strategy, then she pays a cost of $c>0$.

\[
U_C (\varphi; \varepsilon) \ = \ B \int_{0}^R \mathbb{P}(election|\varphi, \varepsilon, \theta) \mu(\theta|\varepsilon) d\mu(\theta) - c \varphi
\]

Finally, the voter's decisions are sequentially rational, in the sense that they are undertaken after the expenditure and investigations are undertaken. They cannot change the decisions ex-post, and this facilitates the decision rules for voters. Ex-ante, I assume that the best is to remove from office the incumbent whenever the challenger credibly shows evidence that the incumbent is corrupt. The chance that the challenger convinces the voter is a function $d(\varepsilon-\theta)$, and to simplify, I consider that this function is equal to $d(\varepsilon-\theta) = \dfrac{\varepsilon-\theta}{R}$. In the appendix, I model the decision for a generic functional form for $d(.)$.

I solve this game for a \textit{Perfect Bayesian Equilibrium} \citep{Fudenberg1991book, Fudenberg1991}, and as this is a signaling game, I also use \textit{universal divinity} as the equilibrium selection criteria \citep{BanksSobel1987}. The restriction imposed by the universal divinity requires that the challenger, facing a deviation from the equilibrium path, assign a probability one on for the type that is more likely to deviate. Moreover, as I have a continuum of possible investment strategies, I use the approach by \citet{Malaith1987}, which consists in finding the monotonicity in the payoffs and single crossing conditions, characterizing the behavior of the types inside the intervals of the type space, analyzing the incentives to pool or separate among the types.

\begin{definition}
 \label{def_eqn}
 A Perfect Bayesian Equilibrium for the strategic interaction described consists in strategic choices of the expenditure $\varepsilon$ and the negative campaign $\varphi$ such that:
 \begin{enumerate}
  \item For an optimal expenditure level, $\theta \in [0,R]$, the proposed expenditure $\varepsilon$ maximizes $U_I (\varepsilon; \varphi, \theta)$.
  \item $\forall \bveps \in \left[0,A \right]^K $ and $\psi \in \{B, \ G \}$, $\bvphi^{*}_j(\bveps, \psi)$ maximizes $ U_j (\bvphi_j; \ \bvphi^{*}_{-j}, \ \bups^{*}, \ \bveps^{*}, \ \mu^*) $, $\forall j \in \{1, \cdots, L\}$
  \item The beliefs are derived using Bayes Rule, whenever possible. The universal divinity also requires that for all expenditure levels that are off-the-equilibrium path, $\mu(\theta| \varepsilon)>0$ (in fact, 1) only if $\widehat{\varepsilon} \in \arg \min_{\theta} p(\theta, \widehat{\varepsilon})$, where $ p(\theta, \widehat{\varepsilon})$ is the profit from deviating from the optimal $\varepsilon$ to a deviation expenditure $\tilde{\varepsilon}$, when the optimal expenditure level is $\theta$.
 \end{enumerate}
\end{definition}

Note that this model has no ideological proximity, or affinity between the voter and any of the politician. This because the paper's objective is to explore the incentives for corruption, not the trade-offs between ideology and corruption.

\subsection{The Solution for the One Incumbent - One Challenger Model}

Applying backward induction, the voters retain the incumbent if the policy result was good and no corruption was exposed. From the challenger's perspective, as there is no cost of entry, she decides whether to invest or not her campaign resources in exposing the incumbent. She does so when the expected utility of exposing is higher than or equal the expected utility of not exposing, given her beliefs about the real value of $\eta$. Thus:

\[
B \int_{t_i \in T} \Prob (\bups = (0,1)\ | \ \eta, \varepsilon^*, \varphi)\mu^*(t_i|\varepsilon^*) d\mu - c \varphi(\psi, \varepsilon^*) \geq 0
\]

Rearranging and applying the fact that $ \Prob(\bups = (0,1) | \varepsilon^*, \varphi ( \psi, \varepsilon^*), \eta) = \varphi(\psi, \varepsilon^*) \lambda(\varepsilon^*-\eta) $ and $\mu^*(t_i | \varepsilon^*) = \mu(\eta) = \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta}$ yields to:

\[
B \varphi(\psi, \varepsilon^*) \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta - c \varphi(\psi, \varepsilon^*)
\]

Isolating $\varphi(\psi, \varepsilon^*)$, let $\lambda_\varepsilon = \int_0^A \lambda(\varepsilon^* - \eta) \dfrac{f(\eta)}{\int_0^{A}f(\eta)d\eta} d\eta$ and $Q(B, c) = \dfrac{c}{B}$. Sequential rationality implies three distinct decisions: first, the challenger exposes the corrupt incumbent for sure whenever $\lambda_\varepsilon > Q(B, c)$; second, the challenger never exposes the corrupt incumbent when $ \lambda_\varepsilon < Q(B, c)$; and finally, the challenger is indifferent between exposing or not the corrupt incumbent when $\lambda_\varepsilon = Q(B, c)$. Optimality suggests that incumbent politicians will calibrate their rent extraction in order to make challengers indifferent between investigating or not.\footnote{To avoid a trivial equilibrium we assume that $Q < \dfrac{\int_0^A \lambda(A - \eta)f(\eta) d\eta}{\int_0^Af(\eta)d\eta} = Q^*$. If $Q \geq Q^*$, then the only equilibrium is to play $A$ regardless of $\eta$, and there will be no exposures.}

In this situation, there exists $\overline{\eta}$ such that:

\[
\lambda_A = \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta)f(\eta) d\eta}{\int_{\overline{\eta}}^Af(\eta)d\eta} = Q(B, c)
\]

This equation represents the upper limit in the incumbent politician's strategy when the randomly drawn optimal expenditure is too close to the maximum expenditure. In these situations is more profitable for them to play $A$. We say that the threshold for this case is $\overline{\eta}$.

Now, let $\delta(\varepsilon)$ the probability function that characterizes the amount of negative campaign chosen by the challenger when $\varepsilon \in [ 0, \ \overline{\eta}]$. The optimal $\varepsilon$ solves the equation $\lambda_\varepsilon = Q(B, c)$, making the challenger indifferent between exposing or not the incumbent's corruption. As $\lambda(.)$ has an inverse function, the optimal strategy for the incumbent is:

\begin{equation*}
\varepsilon^*(\eta) \ = \ \eta + \lambda^{-1}\left(\dfrac{c}{B}\right)
\end{equation*}

Therefore, the optimal strategy for the incumbent politician is to add a kickback $\kappa$ to the cost for providing the public good. The incumbent devises the optimal kickback to make the challenger indifferent between expose or not the corrupt incumbent. The optimal kickback is increasing in the cost of the negative campaign and decreasing in the benefit of holding office.

The incumbent, on the other hand, only plays this strategy when it is incentive compatible for her. To be an optimal response, it should be a $\arg \max$ for $U_I$. Taking the derivative of $U_I$, and setting it to zero gives us the following differential equation for $\delta(\varepsilon)$:

\[
\dfrac{d \delta}{d \varepsilon} + \delta(\varepsilon)\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)} = \frac{1}{B}\frac{u^{'}(\kappa)}{\lambda(\kappa)}
\]

Under the boundary condition $\delta(\kappa)=0$. The equation is a well defined first order differential equation that has a straightforward unique solution determined by the boundary condition. Solving for $\delta(\varepsilon)$, we have:

\[
\delta(\varepsilon) = \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right)
\]

Combining all these results together gives us the following lemma:

\begin{lemma}
 \label{lemma_m1}
 A Perfect Bayesian Equilibrium for the game when there is one incumbent and one challenger is a pair of strategies and beliefs such that the optimal strategies are
 \begin{enumerate}
  \item For the incumbent 
  \[
   \varepsilon^{*}(\eta) \quad = \quad \twopd{\eta + \kappa}{0 \leq \eta \leq \overline{\eta}}{A}{\eta > \overline{\eta}}
  \]
  \item For the challenger
  \[
   \varphi^*(\varepsilon) \quad = \quad \threepdo{0}{\varepsilon < \kappa}{\delta(\varepsilon)}{\kappa \leq \varepsilon \leq \overline{\eta}}{\delta(A)}
  \]
 \item And the voter replaces the incumbent if there is evidence of corruption.
 \end{enumerate}
 Where $\lambda(.)$ is the challenger's campaign technology function. The optimal rent extraction is:
 \[
 \kappa = \lambda^{-1}\left(\dfrac{c}{B}\right)
 \]
 The upper threshold, $\overline{\eta}$, satisfies 
 \[
 \dfrac{\int_{\overline{\eta}}^A \lambda(A - \eta) f(\eta) d\eta}{\int_{\overline{\eta}}^A f(\eta)d\eta} - \dfrac{c}{B} = 0
 \]
 \[
 \delta(\varepsilon) \ = \ \dfrac{u^{'}(\kappa)}{B\lambda^{'}(\kappa)}\left(1 - e^{\frac{\lambda^{'}(\kappa)}{\lambda(\kappa)}(\kappa-\varepsilon)}\right) 
 \]
 And the beliefs are updated using Bayes rule whenever possible.
\end{lemma}

The remainder of the proof and the demonstration that this strategy is indeed an equilibrium is in the Appendix. Note three critical features on this equilibrium. First, an increase in the value of office ($B$) decreases the kickbacks extracted and the amount of negative campaign. Decreases kickbacks because it becomes more profitable to be reelected vis-a-vis extract rents, and lowers the amount of negative campaign because there are fewer opportunities to detect corrupt behavior. Second, increasing the costs of exposing corruption ($c$) increases the kickbacks and decreases the amount of exposure in equilibrium. Finally, increasing the gains from extracting rents (increasing $u'$) does not change the amount of extraction, but increases the amount of negative campaign, as a form to cope with the possibility of deviating from the equilibrium. These results are intuitive but demonstrate that the model follows a reasonable logic.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}